---
title: "Denmark: Boligbyrde"
author: "CAKU"
date: "`r Sys.Date()`"
output: html_document
---

```{r boligbyrde,include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
options(scipen=999)
```

# Denmark: Boligbyrde

```{r }
library(pacman)
pacman::p_load(tidyr,dplyr,ggplot2,boot,openxlsx,lubridate,forcats,broom,purrr,caret,glue,devtools,dkstat,httr,rvest,zoo)
source(file = "money_theme.R")
```

```{r}

df =
  openxlsx::read.xlsx(xlsxFile = "Data/20223617848365363032BM011_2.xlsx",startRow = 3) %>% 
  setNames(.,c("ZIP","DATE","SALES_TYPE","HOUSE","FLAT")) %>% 
  tidyr::fill(ZIP,.direction="down") %>% 
  tidyr::fill(DATE,.direction="down") %>% 
  gather(PROPERTY_TYPE,VALUE,HOUSE,FLAT) %>% 
  filter(!VALUE=="..") %>% 
  dplyr::mutate(VALUE=as.integer(VALUE)) %>% 
  dplyr::mutate(DATE=lubridate::ceiling_date(as.Date(as.yearqtr(DATE, format = "%YK%q")),"quarters")-days(1))

df_m2price = 
  df %>% 
  # filter(ZIP=="2800 Kgs.Lyngby") %>% 
  filter(SALES_TYPE=="Realiseret handelspris") %>% 
  dplyr::select(ZIP,DATE,SALES_TYPE,VALUE,PROPERTY_TYPE) %>% 
  dplyr::rename(STAT=SALES_TYPE)

```

```{r}

source_url = "https://finansdanmark.dk/tal-og-data/boligstatistik/obligationsrenter/"
current_url = xml2::read_html(source_url) %>%
  html_node("#wrapper > div > div.sectionB > div.container > div > div.span8 > p:nth-child(10) > a") %>% 
  rvest::html_attr("href")
xlsx_url = paste0("https://finansdanmark.dk/",current_url)

df_interest = openxlsx::read.xlsx(xlsxFile = xlsx_url,startRow = 3)

df_interest$Date = as.Date(paste(df_interest$År, df_interest$Uge, 1, sep="-"), "%Y-%U-%u")
df_interest = 
  df_interest %>% 
  dplyr::select(Date,Kort.rente,Lang.rente) %>% 
  dplyr::mutate( CurveLongShort = Lang.rente - Kort.rente ) %>% 
  gather(RATE_TYPE,RATE_VALUE,Kort.rente:CurveLongShort) %>% 
  dplyr::rename(DATE=Date) %>% 
  group_by(RATE_TYPE) %>% 
  tidyr::complete(DATE = seq.Date(from = min(DATE,na.rm=T), to = max(DATE,na.rm=T), by="day")) %>% 
  tidyr::fill(RATE_VALUE,.direction="downup") %>% 
  crossing(PROPERTY_TYPE=c("FLAT","HOUSE")) 
  

```


```{r fig.width=10,fig.height=10}

df_m2price %>% 
  filter(ZIP %in% c("2800 Kgs.Lyngby")) %>% 
  inner_join( df_interest ) %>% 
  filter(RATE_TYPE %in% c("Kort.rente","Lang.rente")) %>% 
  dplyr::mutate(RATE_BURDEN=VALUE*(RATE_VALUE/100)) %>% 
  ggplot(.,aes(x=DATE,y=RATE_BURDEN,color=PROPERTY_TYPE)) +
  geom_line() +
  facet_wrap(~RATE_TYPE,ncol=1) +
  scale_x_date(date_breaks = "1 year",date_labels = "%Y") +
  geom_hline(yintercept = 0,linetype=2) +
  theme_money_printer_go_brrr(base_size=12)  +
  labs(title="Boligbyrde: DK Interest Payment per SQMT",
       x="Date",
       y="DKK",
       caption = timestamp_caption()
       )

```

## Household income 30%


```{r fig.width=10,fig.height=10}
#```{r }

df_m2price %>% 
  filter(ZIP %in% c("2800 Kgs.Lyngby")) %>% 
  inner_join( df_interest ) %>% 
  filter(RATE_TYPE %in% c("Kort.rente","Lang.rente")) %>% 
  dplyr::mutate(RATE_BURDEN=180*VALUE*(RATE_VALUE/100)) %>% 
  dplyr::mutate(RATE_BURDEN=RATE_BURDEN/(1/3)) %>% 
  ggplot(.,aes(x=DATE,y=RATE_BURDEN,color=PROPERTY_TYPE)) +
  geom_line() +
  facet_wrap(~RATE_TYPE,ncol=1) +
  scale_x_date(date_breaks = "1 year",date_labels = "%Y") +
  geom_hline(yintercept = 0,linetype=2) +
  theme_money_printer_go_brrr(base_size=12)  +
  labs(title="Boligbyrde: DK Interest Payment per SQMT",
       x="Date",
       y="DKK",
       caption = timestamp_caption()
       )

```
