# Bond ETF chart gallery

Full indicator panels for bond ETFs. Missing symbols are shown as unavailable rather than stopping the book render.

## Bond ETFs

Short:
- SHV: iShares Short Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SHV",currency=="USD"))
```
- TBF: ProShares Short 20+ Yr Treasury
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="TBF",currency=="USD"))
```
- TTT: UltraPro Short 20+ Year Treasury
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="TTT",currency=="USD"))
```
- TBX: Short 7-10 Year Treasury
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="TBX",currency=="USD"))
```
- PST: UltraShort 7-10 Year Treasury
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="PST",currency=="USD"))
```
- TBT: UltraShort 20+ Year Treasury
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="TBT",currency=="USD"))
```

Long:
- MBB: iShares MBS ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="MBB",currency=="USD"))
```
- GOVT: iShares U.S. Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="GOVT",currency=="USD"))
```
- SGOV: iShares 0-3 Month Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SGOV",currency=="USD"))
```
- SHY: iShares 1-3 Year Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SHY",currency=="USD"))
```
- IEI: iShares 3-7 Year Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="IEI",currency=="USD"))
```
- IEF: iShares 7-10 Year Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="IEF",currency=="USD"))
```
- UST: Ultra 7-10 Year Treasury
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="UST",currency=="USD"))
```
- TLH: iShares 10-20 Year Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="TLH",currency=="USD"))
```
- TLT: iShares 20+ Year Treasury Bond ETF
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="TLT",currency=="USD"))
```
- UBT: Ultra 20+ Year Treasury
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="UBT",currency=="USD"))
```

Commodities:
- IAU: iShares Gold Trust
- SLV: iShares Silver Trust
