```{r  include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
options(scipen=999)
```

```{r}

if (!require(pacman)) { install.packages("pacman") }
pacman::p_load(fredr,
               dplyr,
               tidyr,
               lubridate,
               caret,
               partykit,
               pROC,
               gganimate,
               devtools,
               gridExtra,
               httr,
               DT,
               httr,
               glue,
               visNetwork,
               dkstat,
               data.table,
               pROC,
               rPref,
               progress,
               quantmod,
               rvest,
               ggrepel)
source(file = "money_theme.R")

# library("devtools")
# install_github("rOpenGov/dkstat")
library(dkstat)
```

```{r }
readRenviron(path = "Renviron.site")
fredr::fredr_set_key(key = Sys.getenv("FRED_API"))
```

# Equity Markets and the S&P 500

Price index DK

```{r}
# Indexed to 2015
df_PRIS114 = dkstat::dst_get_data(table = "PRIS114",
                     VAREGR = "00 Nettoprisindeks i alt",
                     ENHED = "Indeks",
                     Tid = "*") %>% 
  dplyr::mutate(TID=as.Date(TID)) %>%
  arrange(TID) %>% 
  dplyr::mutate(Index=value/100) %>% 
  tidyr::complete(TID=seq.Date(from=min(TID,na.rm=T),to=Sys.Date(),by="1 day")) %>% 
  tidyr::fill(TID,.direction = "down")  %>% 
  tidyr::fill(value,.direction = "down")   %>% 
  tidyr::fill(VAREGR,.direction = "down")   %>% 
  tidyr::fill(ENHED,.direction = "down")    %>% 
  tidyr::fill(Index,.direction = "down") %>% 
  dplyr::select(TID,value) %>% 
  dplyr::rename(date=TID) %>% 
  dplyr::mutate(series_id="PRICE_INDEX",
                currency="DKK")

```

Price index US

```{r}
df_CPIAUCNS = fredr::fredr("CPIAUCNS") %>% 
    dplyr::select(series_id,
                  date,
                  value) %>% 
    tidyr::complete(date=seq.Date(from=min(date,na.rm=T),to=Sys.Date(),by="1 day")) %>% 
    tidyr::fill(value,.direction = "down") %>% 
    tidyr::fill(series_id,.direction = "down") %>% 
  dplyr::mutate(index=ifelse(date==ymd("2015-01-01"),value,NA)) %>% 
  tidyr::fill(index,.direction = "downup") %>% 
  dplyr::mutate(value=100*value/index,
                series_id="PRICE_INDEX",
                currency="USD") %>% 
  dplyr::select(-index)
```

Index 1 (To keep nominal prices)

```{r}
df_nominal = expand.grid(currency=c("USD","DKK"),
                         value=1,
                         series_id="NOMINAL",
                         date=seq.Date(min(df_CPIAUCNS$date),max(df_CPIAUCNS$date),by="1 day"))
```


Gold price, Silver Price, Oil Price, Bitcoin, USD

```{r}

series_ids_yahoo = unique(c("CL=F",
                            "GC=F",
                            "SI=F",
                            "BTC-USD",
                            "DKKUSD=X",
                            "USDDKK=X"))

df_macro_yahoo = rbindlist(lapply(series_ids_yahoo,function(ticker) {
      temp_df = getSymbols(ticker, env = NULL) %>% 
      as.data.frame(.) %>% 
      dplyr::mutate(Date=row.names(.)) %>% 
      dplyr::mutate(Date=gsub("X","",Date)) %>% 
      dplyr::mutate(Date=ymd(Date)) %>% 
      dplyr::select(c(7,1)) %>% 
      setNames(.,c("date","value")) %>% 
      dplyr::mutate(series_id=ticker) %>% 
      tidyr::complete(date=seq.Date(from=min(date,na.rm=T),to=Sys.Date(),by="1 day")) %>%
      tidyr::fill(value,.direction = "down")  %>%
      tidyr::fill(series_id,.direction = "down")
      
      row.names(temp_df) = NULL
      return( temp_df )
}))

# USD
df_macro_yahoo_usd = df_macro_yahoo %>% 
  filter(!series_id=="USDDKK=X") %>% 
  dplyr::mutate(currency="USD")

# DKK
df_macro_yahoo_dkk = df_macro_yahoo %>% 
  inner_join( df_macro_yahoo %>% filter(series_id=="USDDKK=X") %>% dplyr::select(date,value) %>% dplyr::rename(usd=value)) %>% 
  filter(!series_id=="DKKUSD=X") %>% 
  dplyr::mutate(value=value*usd,
                currency="DKK") %>% 
  dplyr::select(-usd)

df_macros = df_macro_yahoo_usd %>% 
  bind_rows( df_macro_yahoo_dkk ) %>% 
  bind_rows(df_CPIAUCNS) %>% 
  bind_rows(df_PRIS114) %>% 
  bind_rows(df_nominal)

```

Tickers


Short:
- SHV: iShares Short Treasury Bond ETF
- TBF: ProShares Short 20+ Yr Treasury
- TTT: UltraPro Short 20+ Year Treasury
- TBX: Short 7-10 Year Treasury
- PST: UltraShort 7-10 Year Treasury
- TBT: UltraShort 20+ Year Treasury

Long:
- MBB: iShares MBS ETF
- GOVT: iShares U.S. Treasury Bond ETF
- SGOV: iShares 0-3 Month Treasury Bond ETF
- SHY: iShares 1-3 Year Treasury Bond ETF
- IEI: iShares 3-7 Year Treasury Bond ETF
- IEF: iShares 7-10 Year Treasury Bond ETF
- UST: Ultra 7-10 Year Treasury
- TLH: iShares 10-20 Year Treasury Bond ETF
- TLT: iShares 20+ Year Treasury Bond ETF
- UBT: Ultra 20+ Year Treasury

Commodities:
- IAU: iShares Gold Trust
- SLV: iShares Silver Trust

```{r}
series_ids_yahoo = unique(c("GC=F",
                            "SI=F",
                            "BTC-USD",
                            "ETH-USD",
                            # "^RUT",
                            "^W5000",
                            "^IXIC",
                            "^GSPC",
                            
                            "SHV",
                            "TBF",
                            "TTT",
                            "TBX",
                            "PST",
                            "TBT",
                            
                            "XLK",
                            "XLV",
                            "XLY",
                            "XLP",
                            "XLU",
                            "XLF",
                            "XLI",
                            "XLB",
                            "XLE",
                            "XLRE",
                            "XLC",
                            
                            "REW",
                            "RXD",
                            "SCC",
                            "SDP",
                            "SKF",
                            "SIJ",
                            "SMN",
                            "DUG",
                            "SRS",
                            
                            "MBB",
                            "GOVT",
                            "SGOV",
                            "SHY",
                            "IEI",
                            "IEF",
                            "UST",
                            "UBT",
                            "TLH",
                            "TLT",
                            
                            "^OMXC25"))

get_yahoo_ticker = function(ticker, attempts = 3) {
  for (attempt in seq_len(attempts)) {
    temp_df = tryCatch(
      getSymbols(ticker, env = NULL),
      error = function(error) NULL
    )

    if (!is.null(temp_df)) {
      return(
        temp_df %>%
      as.data.frame(.) %>% 
      dplyr::mutate(Date=row.names(.)) %>% 
      dplyr::mutate(Date=gsub("X","",Date)) %>% 
      dplyr::mutate(Date=ymd(Date)) %>% 
      dplyr::select(c(7,1)) %>% 
      setNames(.,c("date","price")) %>% 
      dplyr::mutate(ticker=ticker) %>% 
      tidyr::complete(date=seq.Date(from=min(date,na.rm=T),to=Sys.Date(),by="1 day")) %>%
      tidyr::fill(price,.direction = "down")  %>%
      tidyr::fill(ticker,.direction = "down")
      )
    }

    if (attempt < attempts) Sys.sleep(2 ^ (attempt - 1))
  }

  warning(sprintf("Skipping Yahoo Finance ticker %s after %d failed attempts", ticker, attempts))
  NULL
}

df_tickers_yahoo = rbindlist(lapply(series_ids_yahoo, get_yahoo_ticker), fill = TRUE)
```

```{r}

df_adjusted = df_tickers_yahoo %>% 
  inner_join( df_macros ) %>% 
  dplyr::mutate(index=price/value) %>% 
  dplyr::select(-price,-value)

```

Plot function

```{r}
draw_plots = function(data,lines=NA) {
  if (nrow(data) == 0 || !any(is.finite(data$index))) {
    return(
      ggplot() +
        theme_void() +
        labs(title = "Market data unavailable",
             subtitle = "No usable price history was returned for this ticker")
    )
  }
  
  ticker_ = unique(data$ticker)
  temp_df = data %>% filter(ticker==ticker_)
  
  # Lines
  df_lines = temp_df %>% 
    filter(series_id=="NOMINAL") 
  
  if (unique(!is.na(lines))) {
  df_lines = rbindlist(lapply(seq(length(lines)),function(line) {
    
    df_lines %>% 
      dplyr::mutate(series_id="SUPPORT",
                    predicted=predict(
        df_lines %>% 
          filter(date %in% lines[[line]]) %>% 
          lm(index~date,data=.),
        .)) %>% 
      dplyr::mutate(category=paste0("line",line))
    
  }))
  } else {
  df_lines = data.frame()
  }
  
# All time plot
p1 = temp_df %>% 
  filter(series_id=="NOMINAL") %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  theme(legend.position = "bottom") +
  scale_x_date(date_labels = "%Y",date_breaks = "5 years") +
  scale_y_continuous(limits = c(0,NA)) +
  labs(x=NULL,y=NULL,title=glue("{ticker_}"),subtitle="All Time")
if (nrow(df_lines)>0) {
  p1 = p1 + 
    geom_line(data=df_lines,aes(x=date,y=predicted,color=category,group=category),linetype=2)
}

# Last year
p2 = temp_df %>% 
  filter(series_id=="NOMINAL") %>%  
  filter(date>=Sys.Date()-years(1)) %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  theme(legend.position = "bottom") +
  scale_x_date(date_labels = "%b",date_breaks = "1 month",limits = c(Sys.Date()-years(1),NA)) +
  geom_vline(xintercept = Sys.Date(),linetype=2) +
  labs(x=NULL,y=NULL,subtitle="Last Year")





# Indicator heatmap
indicator_data = temp_df %>%
  filter(series_id=="NOMINAL") %>% 
  arrange((date))

indicator_index <- indicator_data$index
safe_indicator <- function(minimum_observations, calculation) {
  if (sum(is.finite(indicator_index)) < minimum_observations) {
    return(rep(NA_real_, length(indicator_index)))
  }
  tryCatch(calculation(), error = function(error) {
    rep(NA_real_, length(indicator_index))
  })
}

if (sum(is.finite(indicator_index)) < 200) {
  p2b <- ggplot() +
    theme_void() +
    labs(subtitle = "Indicators unavailable: insufficient price history")
} else {
  p2b <- indicator_data %>%
  dplyr::mutate(value_rsi=safe_indicator(15, function() TTR::RSI(indicator_index)),
                value_macd=safe_indicator(26, function() {
                  macd <- TTR::MACD(indicator_index)
                  macd[,1] - macd[,2]
                }),
                value_cci=safe_indicator(20, function() TTR::CCI(indicator_index)),
                value_goldencross=safe_indicator(200, function() {
                  TTR::SMA(indicator_index,n=50) - TTR::SMA(indicator_index,n=200)
                })) %>%
  dplyr::mutate(value_lastdate=ifelse(index<last(index) & !date==max(date),as.Date(date),as.Date(NA))) %>% 
  dplyr::mutate(value_lastdate=if (all(is.na(value_lastdate))) NA_real_ else max(value_lastdate,na.rm=T)) %>%
  dplyr::mutate(value_lastdate=as.numeric(date-as.Date(value_lastdate))) %>% 
  tidyr::fill(value_lastdate,.direction = "down") %>% 
  dplyr::mutate(p_rsi=pnorm(value_rsi,mean=mean(value_rsi,na.rm=T),sd=sd(value_rsi,na.rm=T)),
                p_macd=pnorm(value_macd,mean=mean(value_macd,na.rm=T),sd=sd(value_macd,na.rm=T)),
                p_cci=pnorm(value_cci,mean=mean(value_cci,na.rm=T),sd=sd(value_cci,na.rm=T)),
                p_goldencross=pnorm(value_goldencross,mean=mean(value_goldencross,na.rm=T),sd=sd(value_goldencross,na.rm=T)),
                p_pnorm=pnorm(index,mean=mean(tail(index,3*365),na.rm=T),sd=sd(tail(index,3*365),na.rm=T)), 
                p_lastdate=0.5) %>% 
  filter(date==max(date)) %>% 
  dplyr::select(-currency,-index) %>% 
  gather(stat,val,value_rsi:p_lastdate) %>% 
  separate(stat,into=c("type","metric")) %>% 
  spread(type,val) %>% 
  ggplot(aes(x=metric,y=ticker,fill=p)) +
  geom_tile() +
  geom_text(aes(label=paste0(scales::number(value,0.01)," (",scales::percent(p,0.1),")")),color="white") + 
  scale_fill_gradientn(colours=hcl.colors(10, palette = "ag_GrnYl"),
                       na.value = "transparent",
                       breaks=c(0,0.5,1),
                       labels=c("Minimum",0.5,"Maximum"),
                       limits=c(0,1)) +
  theme_money_printer_go_brrr(12) +
  theme(legend.position="null",
        axis.text.y=element_blank()) +
    labs(x=NULL,y=NULL)
}
  
# SMA
p3 = temp_df %>% 
  filter(series_id=="NOMINAL") %>% 
  arrange(date) %>% 
  dplyr::mutate(sma200=safe_indicator(200, function() TTR::SMA(indicator_index,n=200))) %>%
  dplyr::mutate(index=index-sma200) %>% 
  filter(date>=Sys.Date()-years(1)) %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  scale_x_date(date_labels = "%b",date_breaks = "1 month") +
  geom_hline(yintercept = 0,linetype=2) +
  labs(x=NULL,y=NULL,subtitle="SMA 200")

# RSI
p4 = temp_df %>% 
  filter(series_id=="NOMINAL") %>% 
  arrange(date) %>%
  dplyr::mutate(rsi=safe_indicator(31, function() TTR::RSI(indicator_index,n=30))) %>%
  filter(date>=Sys.Date()-years(1)) %>% 
  ggplot(.,aes(x=date,y=rsi)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  scale_x_date(date_labels = "%b",date_breaks = "1 month") +
  geom_hline(yintercept = c(20,70),linetype=2) +
  labs(x=NULL,y=NULL,subtitle="RSI")

# Real terms (US)
p5 = temp_df %>% 
  filter(series_id=="PRICE_INDEX") %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  scale_x_date(date_labels = "%Y",date_breaks = "1 year") +
  labs(x=NULL,y=NULL,subtitle="Real Terms (US)")

# US Dollars
p6 = temp_df %>% 
  filter(series_id=="USDDKK=X") %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  scale_x_date(date_labels = "%Y",date_breaks = "1 year") +
  labs(x=NULL,y=NULL,subtitle="DKK")

# Oil
p7 = temp_df %>% 
  filter(series_id=="CL=F") %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  scale_x_date(date_labels = "%Y",date_breaks = "1 year") +
  scale_y_continuous(limits=c(0,150)) +
  labs(x=NULL,y=NULL,subtitle="Crude Oil")

# Silver
p8 = temp_df %>% 
  filter(series_id=="SI=F") %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  scale_x_date(date_labels = "%Y",date_breaks = "1 year") +
  labs(x=NULL,y=NULL,subtitle="Silver")

# Gold
p9 = temp_df %>% 
  filter(series_id=="GC=F") %>% 
  ggplot(.,aes(x=date,y=index)) +
  geom_line() +
  theme_money_printer_go_brrr(12) +
  scale_x_date(date_labels = "%Y",date_breaks = "1 year") +
  labs(x=NULL,y=NULL,subtitle="Gold")

  # Index
  p10 = temp_df  %>% 
    filter(series_id %in% c("PRICE_INDEX","NOMINAL")) %>% 
    group_by(series_id) %>% 
    dplyr::mutate(nominal_2015=ifelse(date==ymd("2015-01-01"),index,NA)) %>% 
    tidyr::fill(nominal_2015,.direction = "downup") %>% 
    ungroup() %>% 
    dplyr::mutate(index=100*index/nominal_2015) %>% 
    dplyr::select(-nominal_2015) %>% 
    ggplot(aes(x=date,y=index,color=series_id,group=series_id)) +
    geom_line() +
    theme_money_printer_go_brrr(12) +
    scale_x_date(date_labels = "%Y",date_breaks = "1 year") +
    labs(x=NULL,y=NULL,subtitle="Indexed 2015")

  # Above/below price index
  p11 = temp_df  %>% 
    filter(series_id %in% c("PRICE_INDEX","NOMINAL")) %>% 
    group_by(series_id) %>% 
    dplyr::mutate(nominal_2015=ifelse(date==ymd("2015-01-01"),index,NA)) %>% 
    tidyr::fill(nominal_2015,.direction = "downup") %>% 
    ungroup() %>% 
    dplyr::mutate(index=100*index/nominal_2015) %>% 
    dplyr::select(-nominal_2015) %>% 
    dplyr::mutate(priceindex=ifelse(series_id=="PRICE_INDEX",index,NA)) %>% 
    tidyr::fill(priceindex,.direction = "downup") %>% 
    dplyr::mutate(index=index-priceindex) %>% 
    filter(!series_id=="PRICE_INDEX") %>% 
    ggplot(aes(x=date,y=index,color=series_id,group=series_id)) +
    geom_line() +
    theme_money_printer_go_brrr(12) +
    scale_x_date(date_labels = "%Y",date_breaks = "1 year") +
    labs(x=NULL,y=NULL,subtitle="Above/below price trend") +
    geom_hline(yintercept = 0,linetype=2)

p_all = grid.arrange(p1,p2,p2b,p3,p4,
                     # p5,
                     p6,p7,p8,p9,p10,p11,ncol=1)
print(p_all)

}
```

The snapshots below show the past year of adjusted closing prices from Yahoo Finance. Non-trading days are carried forward. Open the [market](market-chart-gallery.html), [bond ETF](bond-etf-chart-gallery.html), or [sector ETF](sector-etf-chart-gallery.html) gallery for the full indicator panels.

```{r}
draw_market_snapshot <- function(symbol_, currency_, label_) {
  prices <- df_tickers_yahoo %>%
    dplyr::filter(.data$ticker == .env$symbol_,
                  is.finite(.data$price),
                  .data$date >= Sys.Date() - lubridate::years(1)) %>%
    dplyr::arrange(.data$date)

  if (nrow(prices) == 0) {
    return(
      ggplot() +
        theme_void() +
        labs(title = label_,
             subtitle = "Price data unavailable")
    )
  }

  ggplot(prices, aes(x = date, y = price)) +
    geom_line(linewidth = 0.6) +
    theme_money_printer_go_brrr(11) +
    scale_x_date(date_labels = "%b %Y", date_breaks = "3 months") +
    labs(title = label_,
         subtitle = "Adjusted close · past 12 months",
         x = NULL, y = currency_,
         caption = "Source: Yahoo Finance · non-trading days carried forward")
}
```

## S&P 500

```{r fig.width=10,fig.height=3.5}
draw_market_snapshot("^GSPC", "USD", "S&P 500")
```

[Full S&P 500 indicators](market-chart-gallery.html#gallery-sp500)

## Nasdaq

```{r fig.width=10,fig.height=3.5}
draw_market_snapshot("^IXIC", "USD", "Nasdaq Composite")
```

[Full Nasdaq indicators](market-chart-gallery.html#gallery-nasdaq)

## OMX C25

```{r fig.width=10,fig.height=3.5}
draw_market_snapshot("^OMXC25", "DKK", "OMX C25")
```

[Full OMX C25 indicators](market-chart-gallery.html#gallery-omxc25)

## Bitcoin

```{r fig.width=10,fig.height=3.5}
draw_market_snapshot("BTC-USD", "USD", "Bitcoin")
```

[Full Bitcoin indicators](market-chart-gallery.html#gallery-bitcoin)

## Gold

```{r fig.width=10,fig.height=3.5}
draw_market_snapshot("GC=F", "USD", "Gold futures")
```

[Full gold indicators](market-chart-gallery.html#gallery-gold)

## Long Treasury bonds

```{r fig.width=10,fig.height=3.5}
draw_market_snapshot("TLT", "USD", "TLT · long Treasury bond ETF")
```

[Full bond ETF indicators](bond-etf-chart-gallery.html)
