# Sector ETF chart gallery

Full indicator panels for sector ETFs, including short and leveraged funds.

## Sector ETFs

Long:

- Technology: Technology Select Sector SPDR Fund (XLK)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLK",currency=="USD"))
```
- Health Care: Health Care Select Sector SPDR Fund (XLV)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLV",currency=="USD"))
```
- Consumer Discretionary: Consumer Discretionary Select Sector SPDR Fund (XLY)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLY",currency=="USD"))
```
- Consumer Staples: Consumer Staples Select Sector SPDR Fund (XLP)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLP",currency=="USD"))
```
- Utilities: Utilities Select Sector SPDR Fund (XLU)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLU",currency=="USD"))
```
- Financials: Financial Select Sector SPDR Fund (XLF)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLF",currency=="USD"))
```
- Industrials: Industrial Select Sector SPDR Fund (XLI)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLI",currency=="USD"))
```
- Materials: Materials Select Sector SPDR Fund (XLB)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLB",currency=="USD"))
```
- Energy: Energy Select Sector SPDR Fund (XLE)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLE",currency=="USD"))
```
- Real Estate: Real Estate Select Sector SPDR Fund (XLRE)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLRE",currency=="USD"))
```
- Communication Services: Communication Services Select Sector SPDR Fund (XLC)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="XLC",currency=="USD"))
```

Shorts:

Technology Sector: ProShares UltraShort Technology - REW (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="REW",currency=="USD"))
```
Health Care Sector: ProShares UltraShort Health Care - RXD (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="RXD",currency=="USD"))
```
Consumer Discretionary Sector: ProShares UltraShort Consumer Services - SCC (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SCC",currency=="USD"))
```
Utilities Sector: ProShares UltraShort Utilities - SDP (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SDP",currency=="USD"))
```
Financials Sector: ProShares UltraShort Financials - SKF (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SKF",currency=="USD"))
```
Industrials Sector: ProShares UltraShort Industrials - SIJ (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SIJ",currency=="USD"))
```
Materials Sector: ProShares UltraShort Basic Materials - SMN (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SMN",currency=="USD"))
```
Energy Sector: ProShares UltraShort Oil & Gas - DUG (Note: This is 2x leveraged, and specifically targets the oil and gas industry)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="DUG",currency=="USD"))
```
Real Estate Sector: ProShares UltraShort Real Estate - SRS (Note: This is 2x leveraged)
```{r fig.height=25,fig.width=10}
draw_plots(data = df_adjusted %>% filter(ticker=="SRS",currency=="USD"))
```
